Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-14 demystify.tex
updates

\paragraph{Discrimination is not tolerated} Third, higher education in the US take a very strong stance against discrimination, especially at the university level.
Many resources are available to encourage and support students from underrepresented and minority (URM) groups to pursue research, e.g., specific scholarships and fellowships. Faculty in CS are also \emph{very} familiar with and are highly encouraged to support URM students in their group. There are also incentives, such as dedicated funding, to motivate faculty to recruit and mentor URM students (\autoref{sec:urm}).

>>>>

\paragraph{Discrimination is not tolerated} Third, higher education in the US take a very strong stance against discrimination, especially at the university level.
Many resources are available to encourage and support students from minority groups to pursue research, e.g., specific scholarships and fellowships. Faculty in CS are also \emph{very} familiar with and are highly encouraged to support such students in their group. There are also incentives, such as dedicated funding, to motivate faculty to recruit and mentor minority students (\autoref{sec:urm}).
